The limits of self commitment and private paternalism \thanks{}

### 2022-01-29 Tables/Attrition.tex
update tex file

% Table generated by Excel2LaTeX from sheet 'Attrition'
\begin{tabular}{lccccccccc}
\toprule
      & \multicolumn{9}{c}{Attrition Table} \\
\midrule
      &       &       &       &       & \multicolumn{2}{c}{Fee arms} & \multicolumn{2}{c}{Promise arms} &  \\
\midrule
\midrule
      & \multicolumn{1}{p{4.045em}}{Overall} & \multicolumn{1}{p{5.59em}}{Pre-experiment} & \multicolumn{1}{p{6.455em}}{Pre-exp vs Exp (p-value)} & \multicolumn{1}{p{4.045em}}{Control} & \multicolumn{1}{p{5em}}{Forced-fee} & \multicolumn{1}{p{4.045em}}{Choice} & \multicolumn{1}{p{4.045em}}{Forced} & \multicolumn{1}{p{4.045em}}{Choice } & \multicolumn{1}{p{4.045em}}{p-value} \\
\midrule
\midrule
Number of branch-day pawns & 34    & 36    & 0.71  & 31    & 31    & 37    & 32    & 34    & 0.38 \\
      & (0.8) & (1.3) &       & (2.2) & (2.3) & (2.6) & (2.4) & (1.7) &  \\
Survey response rate &       & 0.78  &       & 0.77  & 0.75  & 0.77  & 0.8   & 0.79  & 0.46 \\
      &       & (0.01) &       & (0.02) & (0.03) & (0.02) & (0.02) & (0.02) &  \\
\% ended up pawning &       & 0.98  &       & 0.97  & 0.96  & 0.97  & 0.98  & 0.99  & 0.03 \\
      &       & (0.003) &       & (0.004) & (0.008) & (0.006) & (0.004) & (0.003) &  \\
Number of branch-days & -     & 180   &       & 84    & 80    & 93    & 68    & 82    &  \\
\midrule
Obs   & 13534 & 180   &       & 2585  & 2465  & 3406  & 2143  & 2755  &  \\
\bottomrule
\bottomrule
\end{tabular}%

>>>>

% Table generated by Excel2LaTeX from sheet 'Attrition'
\begin{tabular}{lccccccccc}
\toprule
      & \multicolumn{9}{c}{Attrition Table} \\
\midrule
      &       &       &       &       & \multicolumn{2}{c}{Fee arms} & \multicolumn{2}{c}{Promise arms} &  \\
\midrule
\midrule
      & \multicolumn{1}{p{4.045em}}{Overall} & \multicolumn{1}{p{3.5em}}{Pre-exp} & \multicolumn{1}{p{3.365em}}{p-value} & \multicolumn{1}{p{3.275em}}{Control} & \multicolumn{1}{p{4.775em}}{Forced-fee} & \multicolumn{1}{p{3em}}{Choice} & \multicolumn{1}{p{3em}}{Forced} & \multicolumn{1}{p{3em}}{Choice } & \multicolumn{1}{p{3.365em}}{p-value} \\
\midrule
\midrule
Number of branch-day pawns & 34    & 36    & 0.71  & 31    & 31    & 37    & 32    & 34    & 0.38 \\
      & (0.8) & (1.3) &       & (2.2) & (2.3) & (2.6) & (2.4) & (1.7) &  \\
Survey response rate &       & 0.78  &       & 0.77  & 0.75  & 0.77  & 0.8   & 0.79  & 0.46 \\
      &       & (0.01) &       & (0.02) & (0.03) & (0.02) & (0.02) & (0.02) &  \\
\% ended up pawning &       & 0.98  &       & 0.97  & 0.96  & 0.97  & 0.98  & 0.99  & 0.03 \\
      &       & (0.003) &       & (0.004) & (0.008) & (0.006) & (0.004) & (0.003) &  \\
Number of branch-days & -     & 180   &       & 84    & 80    & 93    & 68    & 82    &  \\
\midrule
Obs   & 13534 & 180   &       & 2585  & 2465  & 3406  & 2143  & 2755  &  \\
\bottomrule
\bottomrule
\end{tabular}%
